---
title: "Data Science with R Lab"
author: "Jah Chaisangmongkon"
date: "July 29, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Before we begin, I recommend setting up working directory to be the directory that contain lab documents so that you don't have to worry about path. This is done by the following commands:

```{r}
working_directory = '/Users/jah/jah/teaching/custom_courses/tdri/labs/'
setwd(working_directory)
```

Then perform the following exercise:

1. Load linear_regression_data.csv into R.

```{r}
df <- read.csv('linear_regression_data.csv')
```

2. We are going to use linear regression to predict house prices. First of all, let's look at the variable we want to predict: SalePrice. Plot and explore variable SalePrice and perform basic preprocessing for the variable.

```{r}
summary(df$SalePrice)
hist(df$SalePrice)
```

3. Explore the data to see what features are available. And perform preprocessing steps.

4. Fit linear regression to the data and to predict SalePrice.

5. We can also predict whether the house price will be in low, medium, or high rank. Load logistic_regression_data.csv and use logistic regression and decision tree to fit the data.
